k-Space Domain Parallel Transmit Pulse Design

### 2020-09-10 Manuscript/Result.tex
Wag all done, need to move to wiley template
wag finalizing for upload

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ErrorMap}
	\caption{\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
	Normalized excitation patterns (top row) and error maps (bottom row) in central axial, sagittal and coronal slices 
	for k-space domain (left) and spatial domain designs (right).}
	\label{fig:ErrorMap}
\end{figure}
Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the reference spatial and k-space domain designs. 
Both designs were performed with 16 parallel threads and the 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
The k-space domain design used patch and inclusion widths of 4.
The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
respectively. 
For both design methods, most of the errors appeared at the edges of the transition band, 
and errors elsewhere were lower than 5\% of the target flip angle. 
This indicates uniform inner volume excitation while maintaining the outer volume intact. 
The parallelized k-space domain design required 2.9 seconds computation versus 31.8 seconds for the spatial domain method, a 91\% decrease.

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ComputationTime}
	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4 cycles/FOV. 
	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 cycles/FOV, and 16 threads.}
	\label{fig:ComputationTime}
\end{figure}
\subsection*{k-Space Algorithm Parameters}
Figure \ref{fig:ComputationTime}a plots mean computation time versus number of parallel threads,
holding the patch and inclusion widths fixed at 4 cycles/FOV. 
The computation time decreased rapidly with increasing thread number up to 12 threads, 
and then plateaued, likely due to the overhead involved in initiating threads after that point.
Based on this result, the number of threads was held fixed at 16 for subsequent designs when off-resonance was not compensated.

@@

\begin{figure}
\centering
\begin{tabular}{c | c}
Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
\hline
$\infty$ & 24.4 \\
8 & 2.73 \\
6 & 1.37 \\
4 & 0.53 \\
2 & 0.14
\end{tabular}
\caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
An inclusion width of $\infty$ corresponds to a full matrix solution.}
\label{fig:wsize}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{L_curve}
	\caption{L-curves for spatial domain and k-space domain pulse designs, 
	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Patch / Inclusion Width = 4' versus `Full Patch'),
	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated $\bm{S}^H\bm{S}$ Matrices' versus
	`Exact $\bm{S}^H\bm{S}$ Matrices').}
	\label{fig:LCurves}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{GibbsRinging}
	\caption{Normalized error maps and RMSE for \textbf{(a)} spatial domain design and \textbf{(c)} k-space domain design with 6 mm iso-resolution, 32$\times$32$\times$24 design grid. Red arrows indicate the Gibbs ringing in low-resolution spatial domain design. \textbf{(b)} Normalized error map for spatial domain design with 3 mm iso-resolution, 64$\times$64$\times$48 design grid.}
	\label{fig:GibbsRing}
\end{figure}

\subsection*{Gibbs Ringing}
Figure \ref{fig:GibbsRing}a shows slices of the excitation error pattern produced by pulses designed by the spatial domain method
on a 32$\times$32$\times$24 grid, which were Bloch-simulated on the original 128$\times$128$\times$96 grid. 
There is significant Gibbs ringing in the pattern (indicated by the red arrows),
and the pulses incur a higher RMSE (4.64\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
(2.66\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (3.00\%; Figure \ref{fig:GibbsRing}c). 
Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
The RMS RF amplitudes of the low resolution designs were both 0.05. 
Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
due to the lower-resolution excitation trajectory. 
From a spatial domain point of view, 
the Gibbs ringing in the low-resolution spatial domain design was caused by the design's inability to observe and limit the ringing in the low-resolution design grid. 
From a k-space domain point of view, the Gibbs ringing in 
Figure \ref{fig:GibbsRing}a was due to implicit circulant end conditions at the edges of excitation k-space in the low-resolution
spatial domain design,
which led RF samples at one edge of k-space to wrap-around and affect target locations at the opposite edge of k-space. 
This effect is mitigated using a high-resolution spatial domain design grid, as illustrated in Figure \ref{fig:GibbsRing}b. 
However, even for a low-resolution k-space domain design there is no wrap-around effect in excitation k-space 
because the trajectory points that are incorporated in the weights solution for each patch of target locations are explicitly specified to be those in the immediate vicinity of 
the target points, without circulant end conditions. 
%Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{ReductionFactor}
	\caption{Normalized error maps and RMSEs for spatial domain design (first row) and k-space domain design (second row), 
	using excitation k-space trajectories with different reduction factors (third row).
	The reduction factors are referenced to the 10 ms trajectory in Figure \ref{fig:Target} (second column).}
	\label{fig:kspace_PTX_Acceleration}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=\textwidth]{OffResonance}
	\caption{
	(a) Normalized off-resonance map containing a Gaussian distortion centered above the frontal sinus, 
	to mimic air-tissue susceptibility difference-induced $B_0$ inhomogeneity.
	(b) Normalized excitation maps and RMSEs for spatial domain design with off-resonance correction (first row), 
	and k-space domain design without and with off-resonance correction (second and third rows).}
	\label{fig:kspace_PTX_B0}
\end{figure}

>>>>

Figure \ref{fig:ErrorMap} shows simulated excitation patterns and error maps for the reference spatial and k-space domain designs. 
Both designs were performed with 16 parallel threads and the 64$\times$64$\times$48 grid size (3 mm isotropic resolution), 
and the excitation patterns were evaluated against the target pattern on a 128$\times$128$\times$96 grid size (1.5 mm iso-resolution). 
The k-space domain design used patch and inclusion widths of 4.
The calculated root-mean-squared errors (RMSEs) were 2.42\% (spatial domain) and 2.68\% (k-space domain), 
respectively. 
For both design methods, most of the errors appeared at the edges of the transition band, 
and errors elsewhere were lower than 5\% of the target flip angle. 
This indicates uniform inner volume excitation while maintaining the outer volume intact. 
The parallelized k-space domain design required 2.9 seconds computation versus 31.8 seconds for the spatial domain method, a 91\% decrease.

\subsection*{k-Space Algorithm Parameters}
Figure \ref{fig:ComputationTime}a plots mean computation time versus number of parallel threads,
holding the patch and inclusion widths fixed at 4 cycles/FOV. 
The computation time decreased rapidly with increasing thread number up to 12 threads, 
and then plateaued, likely due to the overhead involved in initiating threads after that point.
Based on this result, the number of threads was held fixed at 16 for subsequent designs when off-resonance was not compensated.

@@

@@

\subsection*{Gibbs Ringing}
Figure \ref{fig:GibbsRing}a shows slices of the excitation error pattern produced by pulses designed by the spatial domain method
on a 32$\times$32$\times$24 grid, which were Bloch-simulated on the original 128$\times$128$\times$96 grid. 
There is significant Gibbs ringing in the pattern (indicated by the red arrows),
and the pulses incur a higher RMSE (4.64\%) than pulses designed using either the spatial domain method with a finer 64$\times$64$\times$48 grid
(2.66\%; Figure \ref{fig:GibbsRing}b) or the k-space domain method with a 32$\times$32$\times$24 grid (3.00\%; Figure \ref{fig:GibbsRing}c). 
Gibbs ringing is not apparent in either the 64$\times$64$\times$48 spatial domain error pattern or the 32$\times$32$\times$24 k-space domain error pattern. 
The RMS RF amplitudes of the low resolution designs were both 0.005. 
Note that the error of the 64$\times$64$\times$48 spatial domain design is slightly higher than designs presented in other figures
due to the lower-resolution excitation trajectory. 
From a spatial domain point of view, 
the Gibbs ringing in the low-resolution spatial domain design was caused by the design's inability to observe and limit the ringing in the low-resolution design grid. 
From a k-space domain point of view, the Gibbs ringing in 
Figure \ref{fig:GibbsRing}a was due to implicit circulant end conditions at the edges of excitation k-space in the low-resolution
spatial domain design,
which led RF samples at one edge of k-space to wrap-around and affect target locations at the opposite edge of k-space. 
This effect is mitigated using a high-resolution spatial domain design grid, as illustrated in Figure \ref{fig:GibbsRing}b. 
However, even for a low-resolution k-space domain design there is no wrap-around effect in excitation k-space 
because the trajectory points that are incorporated in the weights solution for each patch of target locations are explicitly specified to be those in the immediate vicinity of 
the target points, without circulant end conditions. 
%Particularly, for the instance problems whose patches are at the edges of the k-space FOV, the excitation trajectory points at the other ends of the k-space FOV will not be incorporated into the design.

@@

@@

### 2020-09-10 Manuscript/kPtx_paper.tex
wag finalizing for upload

\title{k-Space Domain Parallel Transmit Pulse Design}
\author{Jun Ma$^{1,2}$, Bernhard Gruber$^{3,4}$, Xinqiang Yan$^{1,5}$, and William A. Grissom$^{1,2,5*}$}
\maketitle
\begin{flushleft}
$^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
$^2$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\
$^3$A. A. Martinos Center for Biomedical Imaging, Massachusetts General Hospital, Harvard Medical School, Charlestown, MA, United States\\
$^4$Division MR Physics, Center for Medical Physics and Biomedical Engineering, Medical University Vienna, Vienna, Austria\\
$^5$Department of Radiology and Radiological Sciences, Vanderbilt University, Nashville, TN, United States\\

@@

\par
Word Count: Approximately 3550 \\
*Corresponding author: \\
Will Grissom\\
Department of Biomedical Engineering\\
Vanderbilt University\\
5824 Stevenson Center\\
Nashville, TN 37235 USA \\
E-mail: will.grissom@vanderbilt.edu \\
Twitter: @wgrissom

@@

\bibliographystyle{unsrt}  % cse doesn't work
\bibliography{kPtx_paper}

>>>>

\title{k-Space Domain Parallel Transmit Pulse Design}
\author{Jun Ma$^{1,2}$, Bernhard Gruber$^{3,4}$, Xinqiang Yan$^{1,5}$, and William A. Grissom$^{1,2,5*}$}
\maketitle
\begin{flushleft}
\vspace{-0.5cm}
$^1$Vanderbilt University Institute of Imaging Science, Nashville, TN, United States\\
$^2$Department of Biomedical Engineering, Vanderbilt University, Nashville, TN, United States\\
$^3$A. A. Martinos Center for Biomedical Imaging, Massachusetts General Hospital, Harvard Medical School, Charlestown, MA, United States\\
$^4$Division MR Physics, Center for Medical Physics and Biomedical Engineering, Medical University Vienna, Vienna, Austria\\
$^5$Department of Radiology and Radiological Sciences, Vanderbilt University, Nashville, TN, United States\\

@@

\par
Word Count: Approximately 5500 \\
*Corresponding author: \\
Will Grissom\\
Department of Biomedical Engineering\\
Vanderbilt University\\
5824 Stevenson Center\\
Nashville, TN 37235 USA \\
E-mail: will.grissom@vanderbilt.edu \\
Twitter: @wgrissom

@@

\bibliographystyle{cse}  % cse doesn't work
\bibliography{kPtx_paper}

\pagebreak
%(Please see main document for caption with intended math typesetting)

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{kspace_PTX_Patch}
	\caption{(a) A target point $\vec{k}_j$ and the nearby trajectory points that are included when calculating 
	RF pulse weight contributions from this point.
	Inclusion width is defined as the distance from each target location $\vec{k}_j$ within which 
	which all trajectory points are considered when solving for the $j$-th column of the design ($\bm{W}$) matrix.
	(b) Calculation of the $\bm{W}$ matrix can be performed column-by-column for each target location $\vec{k}_j$,
	or patches of target points can be solved for jointly. 
	Here the 16 columns of $\bm{W}$ for a 4 $\times$ 4 patch of target points are solved together,
	and an inclusion width of 4 cycles/FOV dictates that all trajectory points within a 12 $\times$ 12 region
	centered on the patch are considered in the calculation.}
	\label{fig:Patch}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=6cm]{kspace_PTX_Coil}
	\caption{The 24-channel loop Tx array that was simulated in a human head model to obtain $B_1^+$ maps. 
	The array has diameter 32 cm and height 28 cm. The 16 cm $\times$ 11 cm rectangular loops are arranged in 3 rows of 8.}
	\label{fig:Coil}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{kSpace_PTX_Pattern_Trajectory}
	\caption{(a) Middle axial, sagittal, and coronal slices of the target excitation pattern used for all pulse designs. 
	(b) The SPINS trajectory used in the designs. 
	(c) 10 ms minimum-time gradient waveforms that produce the SPINS trajectory.}
	\label{fig:Target}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{ErrorMap}
	\caption{ %\textcolor{red}{WAG: I think this is the figure that your example in Github should replicate.}
	Normalized excitation patterns (top row) and error maps (bottom row) in central axial, sagittal and coronal slices 
	for k-space domain (left) and spatial domain designs (right).}
	\label{fig:ErrorMap}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{ComputationTime}
	\caption{(a) k-Space computation time versus number of parallel threads, for patch and inclusion widths of 4 cycles/FOV. 
	(b) Computation time (blue axis) and RMSE (red axis) versus patch width, for an inclusion width of 4 cycles/FOV and 16 threads. 
	(c) Computation time (blue axis) and RMSE (red axis) versus inclusion width, for patch widths of 4 and 8 cycles/FOV, and 16 threads.}
	\label{fig:ComputationTime}
\end{figure}

\begin{figure}
\centering
%\begin{tabular}{c | c}
%Inclusion Width & $\bm{W}$ Matrix Size (GB) \\
%\hline
%$\infty$ & 24.4 \\
%8 & 2.73 \\
%6 & 1.37 \\
%4 & 0.53 \\
%2 & 0.14
%\end{tabular}
\caption{$\bm{W}$ matrix sizes in gigabytes (GB) versus inclusion width in cycles/FOV. 
An inclusion width of $\infty$ corresponds to a full matrix solution.}
\label{fig:wsize}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{L_curve}
	\caption{L-curves for spatial domain and k-space domain pulse designs, 
	repeated across five orders of magnitude of the methods' Tikhonov regularization parameters.
	The k-space domain designs were repeated using patch and inclusion widths of four versus solving for the entire domain at once (`Patch / Inclusion Widths = 4' versus `Patch / Inclusion Widths = $\infty$'),
	and using $B_1^+$ map product interpolation versus phase modulation to each trajectory location (`Interpolated Matrices' versus
	`Exact Matrices').}
	\label{fig:LCurves}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{GibbsRinging}
	\caption{Normalized error maps and RMSEs for 
	(a) pulses designed using a trajectory that reaches 6 mm isotropic resolution
	and the spatial domain algorithm with a 32$\times$32$\times$24 grid, 
	(b) pulses designed using the same trajectory and the spatial domain algorithm with a 64$\times$64$\times$48 grid,  
	and (c) pulses designed using the same trajectory and the k-space domain algorithm with a 32$\times$32$\times$24 design grid. 
	Red arrows indicate Gibbs ringing in the 32$\times$32$\times$24 spatial domain design.}
	\label{fig:GibbsRing}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{ReductionFactor}
	\caption{Normalized error maps and RMSEs for spatial domain design (first row) and k-space domain design (second row), 
	using excitation k-space trajectories with different reduction factors (third row).
	The reduction factors are referenced to the 10 ms trajectory in Figure \ref{fig:Target} (second column).}
	\label{fig:kspace_PTX_Acceleration}
\end{figure}

\begin{figure}
	\centering
	%\includegraphics[width=\textwidth]{OffResonance}
	\caption{
	(a) Normalized off-resonance map containing a Gaussian distortion centered above the frontal sinus, 
	to mimic air-tissue susceptibility difference-induced $B_0$ inhomogeneity.
	(b) Normalized excitation maps and RMSEs for spatial domain design with off-resonance correction (first row), 
	and k-space domain design without and with off-resonance correction (second and third rows).}
	\label{fig:kspace_PTX_B0}
\end{figure}
